---
title: "R Notebook"
output: html_notebook
---

My notes from Dr. Joshua Kerr's Time Series Analysis course at CSU Eastbay, Spring '18.

Simulate and plot an AR2 model.
```{r}
set.seed(413)
ar2 = arima.sim(list(order=c(2,0,0), ar=c(.5,.2)), 2000)
acf(ar2)
pacf(ar2)
```
Simulation of AR1 models with strong positive and negative corelations.
```{r}
set.seed(413)
plot(arima.sim(list(order=c(1,0,0), ar=.9), 100))
plot(arima.sim(list(order=c(1,0,0), ar=-.9), 100))

```

```{r}
library(astsa)
ljj = log(jj)
ts.plot(ljj)
acf(ljj)
pacf(ljj)
```
Time series regression
```{r}
quarters = rep(1:4, 21)
fit1 = lm(ljj ~ time(ljj) + factor(quarters))
summary(fit1)
fitted = ts(fit1$fitted.values, start =1960, freq=4)
ts.plot(ljj, fitted, gpars=list(col=c("black", "red")))
acf(resid(fit1))
pacf(resid(fit1))
```

ARIMA
```{r}
fit2 = arima(ljj, order=c(1, 0, 1))
fit2
```

simulation of arima(1,1,0)
```{r}
set.seed(612)
ts.sim = arima.sim(list(order=c(1,1,0), ar=.8), n=500)
ts.plot(ts.sim)



```

ACF and PACF of the differenced series
```{r}
dif = diff(ts.sim, diff=1)
ts.plot(dif)

acf(dif)
pacf(dif)
```

Fitting an AR1 model to the differenced series
```{r}
wh = arima(ts.sim, order=c(1,1,0))
wh
acf(wh$res)
pacf(wh$res)
```

Forecasting the arima model
```{r}
wh = arima(ts.sim, order=c(1,1,0))
pred = predict(wh, n.ahead=12)
ts.plot(ts.sim, xlim=c(400,600))
lines(pred$pred, col="red")
lines(pred$pred + 1.96*pred$se, col="blue", lty=2)
lines(pred$pred - 1.96*pred$se, col="blue", lty=2)

```

ARMAacf
```{r}
ARMAacf(ar=.8, lag.max=20, pacf=FALSE)
```

Simulation of a arima(1,0,1)
```{r}
set.seed(612)
ts.sim = arima.sim(list(order=c(1,0,1), ar=.8, ma=.8), n=500)
ts.plot(ts.sim)
```

Fitting an AR2 using ar.yw()
```{r}
library(astsa)
rec.yw = ar.yw(rec, order=2)
rec.yw$mean
rec.yw$ar
sqrt(diag(rec.yw$asy.var.coef))
rec.yw$var.pred
rec.pr = predict(rec.yw, n.ahead=24)
rec.pr
```

Fitting AR2 using mle.
```{r}
rec.mle = ar.mle(rec, order=2)
rec.mle$ar
```

Fitting AR2 using ARIMA()
```{r}
arima(rec, order=c(2,0,0))
```

```{r}
acf(rec.yw$resid, na.action=na.pass)
acf(rec.mle$resid, na.action=na.pass)
```

Seasonal ARIMA (SARIMA) w/ fed data
```{r}
ts.plot(prodn)
fed.fit = arima(prodn, order=c(1,1,1), seasonal=list(order=c(2,1,1), period=12))
fed.fit
tsdiag(fed.fit, fog.lag=48)
pacf(fed.fit$residuals)
fed.pr = predict(fed.fit, n.ahead=24)
fed.pr
```

SARIMA using sarima() and sarima.for()
```{r}
fed.fit2 = sarima(prodn, 1,1,1,2,1,1,12, no.constant=TRUE)
fed.pr2 = sarima.for(prodn, 24, 1,1,1,2,1,1,12)
```

SARIMA (Air Passenger Miles)
```{r}
library(fma)
library(astsa)
plot.ts(log(airpass))
fit = sarima(log(airpass),0,1,1,0,1,1,12)
```

Simple Exponential Smoothing
```{r}
library(astsa)
plot(AirPassengers)
hw = HoltWinters(rec, gamma=FALSE, beta=FALSE)
plot(hw)
s = sqrt(hw$SSE/(length(soi)-1))
pr = predict(hw, n.ahead=50, prediction.interval = TRUE)
plot(hw, pr)
```
Holt Exponential Smoothing (non-constant growth rate)
```{r}
hw = HoltWinters(rec, beta=TRUE, gamma=FALSE)
plot(hw)
hw
pr = predict(hw, n.ahead=50, prediction.interval = TRUE)
plot(hw, pr)
```

Hold-Winters Exponential Smoothing (non-constant growthrate plus seasonality)
```{r}
hw = HoltWinters(AirPassengers)
plot(hw)
pr = predict(hw, n.ahead=50, prediction.interval = TRUE)
plot(hw, pr)
hw$alpha
hw$beta
hw$gamma
```

```{r}
ts.plot(rec)
acf(rec)
pacf(rec)
fit1 = arima(rec, order=c(2,0,0),
             seasonal=list(order=c(2,0,0)))
acf(fit1$res)
pacf(fit1$res)
```

